\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-02 challenge.tex
start lang-design

\noindentparagraph{%
\headinglabel{C2}{chg:override-v-dependent}.\,
Overriding vs.\ dependent typing.%
}

@@

\noindentparagraph{%
\headinglabel{C3}{chg:self-v-consistency}.\,
Self reference vs.\ logical consistency.%
}

>>>>

\noindentparagraph{%
\headinglabel{C2}{chg:self-v-consistency}.\,
Self reference vs.\ logical consistency.%
}

\noindentparagraph{%
\headinglabel{C3}{chg:override-v-dependent}.\,
Overriding vs.\ dependent typing.%
}

@@

### 2022-10-02 lang-design.tex
start lang-design

We demonstrate the key ingredients of our design as a plugin to the Coq proof assistant,
though we believe our design could be adapted to other proof assistants such as Lean.

>>>>

We use a plugin to the Coq proof assistant to demonstrate the key
ingredients of our design,
though we believe our design could be adapted to other proof assistants such as Lean.

\cref{fig:stlc-mechanized} shows how STLC and its extension with
fixpoints can be mechanized using our plugin, in a style envisioned in
\cref{fig:stlc-nonmechanized}.
The base family "STLC" hosts the STLC metatheories, from abstract syntax
to the type-safety theorem.
Family "STLC_fix", derived from "STLC", makes adjustments as needed by a fixpoints extension:
it adds new constructors to the inductive types ("FInductive") and
adds new cases to the recursive functions ("FRecursion") and induction proofs ("FInduction").
Existing constructors and cases, as well as those definitions and
theorems that need no adjustments ("ty", "env", "empty", "steps", and
"typesafe"), are automatically inherited and reused.

\noindentparagraph{Inductive types are extensible.}

In family "SLTC_fix", inductive type "tm" is formed by the four
constructors inherited from "STLC" and a fifth constructor "tm_fix".

Crucially, the types of the constructors are polymorphic to their enclosing family.
For example, although "tm_app" is defined in the base family,
it can be used to construct applications of fixpoints in the derived family:
%such as \lstinline[mathescape]{tm_app (tm_fix "f" (tm_abs "x" $\dadada$)) tm_unit},
its type \lstinline{tm -> tm -> tm} says "tm_app" can be applied to any
Gallina terms of type "tm",
which in family "SLTC_fix" include those constructed from "tm_fix".

\noindentparagraph{Induction remains exhaustive.}

### 2022-10-02 stlc-mechanized.tex
start lang-design

@@

FInductive tm : Set :=[@\hfill\codecomment{Terms}@]
| tm_var  : id -> tm
| tm_unit : tm
| tm_abs  : id -> tm -> tm
| tm_app  : tm -> tm -> tm.

@@

\end{multicols}
\end{minipage}
\caption{Using our plugin to mechanize STLC and the fixpoints extension
as depicted in \cref{fig:stlc-nonmechanized}.}
\label{fig:stlc-mechanized}
\end{figure}

>>>>

\lstset{
  basicstyle=\fontsize{8}{8.5}\ttfamily,
}

@@

FInductive tm : Set :=[@\hfill\codecomment{Terms}@]
| tm_var  : id -> tm
| tm_unit : tm
| tm_abs  : id -> tm -> tm
| tm_app  : tm -> tm -> tm.[@\label{line:tm-app}@]

@@

\end{multicols}
\end{minipage}
\caption{Using our plugin to mechanize STLC and the fixpoints extension,
as envisioned in \cref{fig:stlc-nonmechanized}.}
\label{fig:stlc-mechanized}
\end{figure}
